Exploration in Target Speaker Extraction using Discrete Tokens and Language Models\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-02 src/paper.tex
update

\title{Exploration in Target Speaker Separation using Discrete Tokens and Language Models\\
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{IEEEkeywords}
target speaker separation, language models, audio discretization
\end{IEEEkeywords}

\section{Introduction}
Speech separation is a fundamental task in separating two speakers' voices from a mixture.

>>>>

\title{Exploration in Target Speaker Extraction using Discrete Tokens and Language Models\\
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{IEEEkeywords}
target speaker extraction, speech separation, language models, audio discretization
\end{IEEEkeywords}

\section{Introduction}
Speech separation, the so-called cocktail party problem \cite{cocktail}, focuses on separating each individual speaker's source from a mixture with multiple speakers.
In real life, speech signals are usually companied with background noise or other speakers' speeches. 
Our humans might grasp the speech but machine is not the case.
These signals may not be optimal for tasks like speaker verification. 
Target speaker extraction is a sub-task of speech separation.
